Independent Component Analysis

### 2022-04-29 paper.tex
added the sound wave example in script, added some texts in the paper.tex regarding information theoretic approach

@@

@@

1) Optimizing Kurtosis (high-order based moment approach) (Mick)
2) non-gaussianity  (Mick)
3) Maximum likelihood estimation (Kannan)
    - Minimizing mutual information (min KL divergence)

>>>>

Several necessay conditions for ICA: 
1) The number of sensors is larger than number of sources. This ensures that the mixing matrix is full rank.
2) THe sources at each sample (time) are mutually independent.
3) At most one source is normally distributed.

@@

1) Non-Gaussianity maximization approach

@@

%1) Optimizing Kurtosis (high-order based moment approach) (Mick)
%2) non-gaussianity  (Mick)
%3) Maximum likelihood estimation (Kannan)
%    - Minimizing mutual information (min KL divergence)

2) Minimize mutual information, max negentropy, and maximum likelihood

Apart fomr the non-Gaussianity based approaches, there are several information theoetic formulations. Here in this section, we will review all different information theoretic frameworks and show that essentially they are equivalent. Then we will talk about the learning rules for these theoretical formulations.

We can first consider the basic idea of minimizing mutual information, which is defined as the KL divergence of the multivariate distribution of the observed data $\bf{x}$ and product of all its marginal distributions, i.e. 
\begin{equation}
I(\bf{x}) = \sum_{\bf{x}}p(\bf{x})\log\frac{p(\bf{x})}{\prod_{i}p_{i}(x_{i})}
\end{equation}. $I(\bf{x})$ is non-negative and is 0 if an only if the $\bf{x}$ are independent. Within this framework, several different approaches have been formulated in history. One of them is a key finding in neural networks, that is maximizing information between inputs $\bf{x}$ and outputs $\bf{y}$ implies that the output distributions are factorized, thus minimizes the mutual information in the outputs $\bf{y}$. Maximizing the output entropy is to maximize $H(\bf{y}) = \sum_{i}H(y_{i}) - I(\bf{y})$. In a neural network, there is a non-linear activation function that generates the output $\bf{y} = g(\bf{u})$. This nonlinearity indeed brings the information of higher order statistics into the optimization process.
